---
title: "Iris: Sepal-Ratio Modeling"
author: "Bastiaan Quast"
date: "Thursday, July 18, 2014"
output:
  ioslides_presentation:
    transition: faster
runtime: shiny
---


# We want to model sepal ratios, do we need separate models for each species?


## Iris dataset

- Included in R package **datasets**
- Originally by Fisher or Anderson
- Measurements for **petal** and **sepal** width and length
- Fifty flowers of three species
    - Setosa
    - Versicolor
    - Virginica


## LOESS Model

 - **Lo**cally W**e**ighted **S**catterplot **S**moothing
    - [more info on LOESS](http://en.wikipedia.org/wiki/Local_regression)
 - General model and species-specific models
    - Standard Error bands
    - Grey band for general model
    - Coloured bands for respective species
 - Adjustable 'wobblyness' of models
 - Adjustable point size and opacity


## Results
```{r echo=FALSE, message=FALSE}
library(knitr)
library(ggvis)
library(shiny)
library(dplyr)
```

```{r, echo = FALSE, message = FALSE, fig.width = 6, fig.height = 4}
iris %>%
  ggvis(~Sepal.Width, ~Sepal.Length) %>%
  layer_smooths(span = input_slider(0.5, 1, 0.5, label = 'General Model'), se = TRUE) %>%
  group_by(Species) %>%
  layer_points(size := input_slider(10, 1000, 100, label = 'Point Size'), opacity := input_slider(0.5, 1, 0.5, label = 'Point Opacity'), fill = ~Species) %>%
  layer_smooths(span = input_slider(10, 1000, 100, label = 'Species Models'), fill = ~Species, se=TRUE) %>%
  add_axis("x", title = "Sepal Width") %>%
  add_axis("y", title = "Sepal Length") %>%
  bind_shiny("ggvis", "ggvis_ui"
             )
```